Bayesian neural networks for sparse coding

### 2018-10-23 icassp_2019/paper.tex
minor

 If the matrix $\mathbf{S}$ and vector $\widehat{\boldsymbol\beta}_{l-1}$ are assumed to be mutually independent, then according to the Central Limit Theorem $[ \mathbf{e}_l ]_d$ can be approximated as a Gaussian-distributed variable when $D$ is sufficiently large. The parameters of the of the approximating Gaussian distribution are set to the marginal mean and variance given in~(\ref{eq:e_moments}).

>>>>

 According to the Central Limit Theorem $[ \mathbf{e}_l ]_d$ can be approximated as a Gaussian-distributed variable when $D$ is sufficiently large. The parameters of the of the approximating Gaussian distribution are set to the marginal mean and variance given in~(\ref{eq:e_moments}).
